\section{Differences From Existing Solutions}\label{sec:diff}

Taiwan's current ecosystem is an \emph{awareness} stack; CarbonPass is the
missing \emph{execution} layer. The audit below was verified instrument by
instrument in July 2026.

\begin{table}[htbp]
\caption{Capability audit: what exists, and what none of it does}
\label{tab:gap}
\small
\begin{tabularx}{\textwidth}{@{}p{0.27\textwidth}p{0.33\textwidth}X@{}}
\toprule
\textbf{Instrument} & \textbf{What it does} & \textbf{What it does not do} \\
\midrule
CAAS ``SME Carbon Reduction Service Station'' (MOEA)\cite{caas} & Courses, articles, referrals & No computation; not a reporting tool \\
IDB Carbon Emissions Calculator (MOEA)\cite{idb} & Rough annual company-level CO$_2$e from bills & No product-level allocation, no CN codes, no CBAM format \\
MOENV CBAM Help Platform (Mar 2026)\cite{tpt-cbam} & Information and consultation & Explicitly informational; computes nothing \\
Taipower app / eBill\cite{taipower} & Consumption charts, tariff simulation & No emissions conversion, no compliance artifacts \\
tre100 pledge platform (CIER)\cite{tre100} & Renewable-energy commitments registry & No measurement tooling \\
Consultants / ESG software\cite{chanchin} & Real one-off ISO certificates & Per-engagement pricing; cannot serve recurring per-product demands across 2,600 firms \\
\bottomrule
\end{tabularx}
\end{table}

\textbf{CarbonPass's difference in one sentence:} it is the only tool that
converts SME-native documents into importer-ready, verifier-structured,
per-CN-code emissions data --- repeatably, in the owner's own language, at
near-zero marginal cost --- and it is designed for \emph{integration} with the
government's existing platforms rather than competition with them.

\section{Expected Benefits (Quantified)}\label{sec:benefits}

\begin{table}[htbp]
\caption{Expected benefits, with basis of estimate}
\label{tab:benefits}
\small
\begin{tabularx}{\textwidth}{@{}p{0.34\textwidth}Xp{0.22\textwidth}@{}}
\toprule
\textbf{Benefit} & \textbf{Quantification} & \textbf{Basis} \\
\midrule
CBAM cost avoided per tonne of product & EUR $\approx$300--600/t (verified $\approx$150 vs.\ defaults 450--750, rising with markups) & Official price\cite{ecprice}; industry multiples\cite{specialinsert} \\
Compliance labor per data pack & Hours instead of consultant-weeks; recurring at near-zero marginal cost & Cluster ISO precedents priced per engagement\cite{chanchin} \\
Energy cost reduction via load shifting & Peak/off-peak tariff spread of several$\times$ on shiftable loads (est.\ 5--15\% of bill for furnace-heavy plants; measured in pilot) & Taipower TOU schedules\cite{taipower}; pilot to verify \\
Emissions reduction & Measured on-meter, logged to ledger; every avoided tonne also cuts the buyer's certificate cost & Grid EF 0.474 kgCO$_2$e/kWh\cite{moeaea} \\
Population served at beachhead & 2,600 CBAM-exposed SMEs; $\sim$1,800-firm cluster; top-3 world export industry & MOENV\cite{tpt-cbam}; \cite{goebel,ktimes} \\
National alignment & Supports NDC 3.0 (--38\%$\pm$2\% by 2035) by extending measurement into the SME layer & \cite{ndc} \\
\bottomrule
\end{tabularx}
\end{table}

\textbf{Corresponding SDGs:} SDG~8 (protecting decent work in an export
cluster), SDG~9 (industry, innovation and infrastructure), SDG~12 (responsible
production), SDG~13 (climate action).

\section{Open Data: Used, Improved, and Given Back}\label{sec:opendata}

Open data is this competition's founding ethos, and the application form asks
three questions of every entry\cite{handbook}. Our answers:

\textbf{Used.} MOENV carbon-footprint emission coefficients
(\href{https://data.gov.tw/en/datasets/28176}{data.gov.tw \#28176}, OpenAPI);
Taiwan product carbon-footprint registry
(\href{https://data.gov.tw/en/datasets/8992}{\#8992}); Taipower generation by
unit at 10-minute resolution
(\href{https://data.gov.tw/en/datasets/8931}{\#8931},
\href{https://data.gov.tw/en/datasets/37331}{\#37331}); Taipower tariff
schedules\cite{taipower}; the MOEA electricity emission factor\cite{moeaea};
EU-published CBAM methodology, default values and certificate
prices\cite{taxud,ecprice}.

\textbf{Suggested improvements.} (1) Publish an official hourly
grid-carbon-intensity series (today it must be derived from the 10-minute unit
feed); (2) publish MOENV emission coefficients mapped to customs (CN/HS)
codes, so any exporter can find the factors relevant to a tariff line; (3)
provide machine-readable Taipower bill formats to enable consented,
automated ingestion.

\textbf{Given back.} CarbonPass will publish (1) a cleaned, documented hourly
Taiwan grid-carbon-intensity dataset derived from \#8931/\#37331, and (2) an
anonymized fastener-sector embedded-emissions benchmark from the pilot ---
both openly licensed, both useful far beyond this project.

\textbf{Open source.} The intent is to release the compliance rules engine and
the grid-intensity pipeline under an open license --- the components with the
greatest public-good value --- consistent with the competition's open-source
encouragement\cite{handbook}.
