\section{Maturity, Implementation, and Verification Plan}\label{sec:maturity}

\textbf{Development stage.} Early prototype, purpose-built for this
competition (no prior commercialization; no modification-rule exposure). At
submission: Module~1 demonstrated end-to-end on a three-firm mock corpus of
real Taiwanese bill and invoice formats; the grid-aware scheduler running on a
synthetic fastener-plant load profile against the \emph{live} open 10-minute
grid feed\cite{taipowerdata}; the LINE conversational front end operational;
demonstration video submitted with the application.

\textbf{Validation plan --- built on the campaign's own machinery.} The
mentorship period is used exactly as the Handbook designs it\cite{handbook}:

\begin{table}[htbp]
\caption{Implementation and verification milestones mapped to the official calendar}
\label{tab:plan}
\small
\begin{tabularx}{\textwidth}{@{}p{0.26\textwidth}X@{}}
\toprule
\textbf{Window (Handbook)} & \textbf{Milestone} \\
\midrule
By 31 Jul 2026 (submission) & PoC v0 + demo video + this proposal; outreach opened to TIFI member firms, MIRDC, and Kaohsiung EPB's voluntary-reduction advisory team as validation partners \\
Aug (preliminary review) & --- \\
Mid-Sep -- mid-Oct (mentorship) & One pilot factory in Gangshan: real bills in, real data pack out; pack structure reviewed with an MIRDC engineer or accredited verifier; one flexible load shifted and measured on-meter; weekly progress log \\
Late Oct (final review) & Live demonstration: data pack generated on stage from raw documents; live grid-aware schedule; pilot before/after ledger; updated market outlook incorporating the September European Parliament vote\cite{akin} \\
\bottomrule
\end{tabularx}
\end{table}

\textbf{Honest boundaries, stated up front.} CarbonPass prepares verification;
it does not replace the accredited verifier\cite{omm}. Preferential carbon-fee
rates belong to large regulated emitters, not SMEs --- the SME's incentives
are customer retention, cost pass-through, energy savings, and
readiness\cite{moenvfee}. The 2028 scope extension is pending legislation and
is treated as a tracked roadmap event, not a booked benefit\cite{akin}. We
believe this candor is itself a feature: under a rubric that weights
feasibility above all\cite{handbook}, a jury should never have to discount our
numbers.

\section{Future Plans: From One District to a Global Answer}\label{sec:future}

\textbf{2026--2027 (Taiwan, beachhead).} Harden the pilot into a
cluster-scale rollout with TIFI/MIRDC; propose integration of the computation
layer into MOENV's CBAM help platform and SMESA's CAAS service
network\cite{tpt-cbam,caas}; publish the open datasets and open-source
components.

\textbf{2027--2028 (regulatory expansion).} If the European Parliament
confirms the downstream extension, onboard the newly covered categories ---
springs, wire, hand tools, household metal articles --- from the same
engine\cite{akin}; extend outputs toward Digital Product Passport payloads as
ESPR phases in\cite{espr}; support SMEs entering Taiwan's lowered carbon-fee
threshold and ETS pilot era\cite{ecobiz}.

\textbf{2028+ (Taiwan can help).} The carbon data wall is not Taiwan's alone:
every SME-exporting economy --- Vietnam, Thailand, Malaysia, India --- faces
the same mechanism with even thinner tooling. CarbonPass's architecture
(open-data grid signal, local-first document AI, EU-format output) is
portable by design. As past Presidential Hackathon winners carried Taiwanese
civic technology to the world, this entry is built to export a Taiwanese
answer to a global problem --- digital inclusion as trade policy,
made in Taiwan.

\section{Team and Eligibility}\label{sec:team}

The team will comprise 3--10 members spanning machine learning, energy systems,
regulatory analysis and fastener-industry domain expertise, including at least
one member of non-ROC nationality, with two designated contacts, per the
Handbook's eligibility rules\cite{handbook}. All development, documentation and
presentation are in English. The entry is original work, created for this
competition; team intellectual-property arrangements follow the Handbook's
terms, and the team commits to full participation in mentorship, presentations
and follow-up benefit tracking. \emph{[Member names, nationalities and contact
details to be completed in the online application form.]}

\vspace{4mm}
\begin{center}
\begin{minipage}{0.86\textwidth}
\centering\itshape
Seven years ago this competition showed that open data could expose corruption.
Three years ago it showed AI could give hearing to the deaf. In 2026, let it
show that a photograph of an electricity bill, met by the right AI, can keep
two thousand six hundred family factories --- and the district they built ---
inside the world economy.
\end{minipage}
\end{center}
