\clearpage
\phantomsection
\addcontentsline{toc}{section}{References}
\footnotesize
\begin{thebibliography}{99}\setlength{\itemsep}{2pt}

\bibitem{tpt-cbam} Yeh, E. (2026, March 2). MOENV to set up CBAM help platform
for SMEs. \emph{Taipei Times}.
\href{https://www.taipeitimes.com/News/taiwan/archives/2026/03/02/2003853116}{taipeitimes.com/News/taiwan/archives/2026/03/02/2003853116}

\bibitem{focus} Focus Taiwan / CNA. (2026, June 3). Taiwan collects nearly
NT\$5 billion in first carbon fee cycle: MOENV.
\href{https://focustaiwan.tw/business/202606030008}{focustaiwan.tw/business/202606030008}

\bibitem{tptfee} Taipei Times. (2026, June 4). First carbon fee cycle rakes in
almost NT\$5bn.
\href{https://www.taipeitimes.com/News/front/archives/2026/06/04/2003858496}{taipeitimes.com/News/front/archives/2026/06/04/2003858496}

\bibitem{moenvfee} Ministry of Environment, ROC (Taiwan). Taiwan's Ministry of
Environment announces ``Fee-Charging Rates of Carbon Fees.''
\href{https://www.moenv.gov.tw/en/news/press-releases/31552.html}{moenv.gov.tw/en/news/press-releases/31552.html}

\bibitem{reset} RESET Carbon. (2025). Taiwan's carbon fee to begin collection
in 2026: Market implications of preferential rates and carbon leakage risk
adjustments.
\href{https://resetcarbon.com/en/taiwans-carbon-fee-to-begin-collection-in-2026-market-implications-of-preferential-rates-and-carbon-leakage-risk-adjustments/}{resetcarbon.com}

\bibitem{taxud} European Commission, DG Taxation and Customs Union. Carbon
Border Adjustment Mechanism.
\href{https://taxation-customs.ec.europa.eu/carbon-border-adjustment-mechanism_en}{taxation-customs.ec.europa.eu/carbon-border-adjustment-mechanism\_en}

\bibitem{icap} International Carbon Action Partnership. (2025, October). EU
adopts simplifications of CBAM rules ahead of the compliance phase starting in
2026.
\href{https://icapcarbonaction.com/en/news/eu-adopts-simplifications-cbam-rules-ahead-compliance-phase-starting-2026}{icapcarbonaction.com}

\bibitem{omm} O'Melveny \& Myers LLP. (2026). How the EU's new default
emissions values under CBAM impact US exporters: What you need to know for
2026.
\href{https://www.omm.com/insights/alerts-publications/how-the-eu-s-new-default-emissions-values-under-cbam-impact-us-exporters-what-you-need-to-know-for-2026/}{omm.com/insights}

\bibitem{bpc} Bipartisan Policy Center. (2026). High CBAM default values
underscore the need for U.S. data.
\href{https://bipartisanpolicy.org/article/high-cbam-default-values-underscore-the-need-for-u-s-data/}{bipartisanpolicy.org}

\bibitem{akin} Akin Gump Strauss Hauer \& Feld LLP. (2026, January). EU Carbon
Border Adjustment Mechanism: Financial obligations commence amid proposed scope
expansion to include new downstream products.
\href{https://www.akingump.com/en/insights/alerts/eu-carbon-border-adjustment-mechanism-financial-obligations-commence-amid-proposed-scope-expansion-to-include-new-downstream-products}{akingump.com/en/insights}

\bibitem{moea} Small and Medium Enterprise and Startup Administration, MOEA.
(2025). 2025 White Paper highlights vital role of small and medium enterprises
in Taiwan's economy.
\href{https://www.sme.gov.tw/article-en-2442-14150}{sme.gov.tw/article-en-2442-14150}

\bibitem{ktimes} Kaohsiung Times. (2026). South Taiwan ``Kingdom of Screws''
accelerates green shift ahead of April global summit.
\href{https://www.kaohsiungtimes.com/south-taiwan-kingdom-of-screws-accelerates-green-shift-ahead-of-april-global-summit-at-the-kaohsiung-exhibition-center/}{kaohsiungtimes.com}

\bibitem{cw} CommonWealth Magazine. (2023, July 12). The screw triggering a
battle worth NT\$200 billion.
\href{https://english.cw.com.tw/article/article.action?id=3462}{english.cw.com.tw/article/article.action?id=3462}

\bibitem{tsmc} TSMC ESG. (2024). TSMC subsidizes suppliers for carbon
reduction, driving green investments worth NT\$5.5 billion.
\href{https://esg.tsmc.com/en-US/articles/343}{esg.tsmc.com/en-US/articles/343}

\bibitem{carbonchain} CarbonChain. Quick guide to EU CBAM goods and CN codes.
\href{https://www.carbonchain.com/cbam/eu-cbam-cn-codes}{carbonchain.com/cbam/eu-cbam-cn-codes}

\bibitem{goebel} Goebel Fasteners / PR Newswire. (2024). Taiwan's fasteners:
The backbone of U.S. industries.
\href{https://www.goebelfasteners.com/taiwans-fasteners-the-backbone-of-us-industries/}{goebelfasteners.com}

\bibitem{specialinsert} Special Insert. (2026, April 23). The fastener industry
faces the CBAM challenge.
\href{https://www.specialinsert.it/en/2026/04/23/fastener-industry-carbon-border-adjustment-mechanism-cbam/}{specialinsert.it}

\bibitem{caas} Small and Medium Enterprise and Startup Administration, MOEA.
Carbon as a Service (CAAS) --- SME Carbon Reduction Service Station.
\href{https://www.sme.gov.tw/caas_en/masterpage-caas_en}{sme.gov.tw/caas\_en}

\bibitem{taipower} Taiwan Power Company. AMI data applications --- Taipower
Smart Grid; rate schedules.
\href{https://smartgrid.taipower.com.tw/en/Data_Analytics/AMI_Data_Applications}{smartgrid.taipower.com.tw};
\href{https://www.taipower.com.tw/2764/2765/2801/}{taipower.com.tw/2764/2765/2801}

\bibitem{idb} Ministry of Economic Affairs, ROC (Taiwan). The carbon emissions
calculator, an IDB new released tool to support enterprises' control on carbon
emissions.
\href{https://www.moea.gov.tw/MNS/english/news/News.aspx?kind=6&menu_id=176&news_id=102426}{moea.gov.tw/MNS/english/news}

\bibitem{ndc} Ministry of Environment, ROC (Taiwan). (2025). Ministry of
Environment announces Taiwan's 2035 Nationally Determined Contribution
(NDC 3.0).
\href{https://www.moenv.gov.tw/en/news/press-releases/34357.html}{moenv.gov.tw/en/news/press-releases/34357.html}

\bibitem{moeaea} Energy Administration, Ministry of Economic Affairs, ROC
(Taiwan). Electricity carbon emission factor.
\href{https://www.moeaea.gov.tw/ECW/English/content/Content.aspx?menu_id=24200}{moeaea.gov.tw/ECW/English}

\bibitem{ecprice} European Commission, DG Taxation and Customs Union. Price of
CBAM certificates.
\href{https://taxation-customs.ec.europa.eu/carbon-border-adjustment-mechanism/price-cbam-certificates_en}{taxation-customs.ec.europa.eu/.../price-cbam-certificates\_en}

\bibitem{fwexport} Fastener World Magazine. (2025). Outlook report on Taiwan's
fastener export momentum (no.~211/213).
\href{https://www.fastener-world.com/data/pdf_download/FW_211_E_251.pdf}{fastener-world.com (PDF)}

\bibitem{tre100} Chung-Hua Institution for Economic Research. (2025, December).
New initiative, tre100, bridges gap between Taiwanese businesses and global
RE100 standards.
\href{https://www.cier.edu.tw/en/institution-en/29908/}{cier.edu.tw/en/institution-en/29908}

\bibitem{taipowerdata} Government Open Data Platform, Taiwan. Taiwan Power
Company --- real-time and historical generation by unit (10-minute).
\href{https://data.gov.tw/en/datasets/8931}{data.gov.tw/en/datasets/8931};
\href{https://data.gov.tw/en/datasets/37331}{data.gov.tw/en/datasets/37331}

\bibitem{espr} European Union. Ecodesign for Sustainable Products Regulation
(EU) 2024/1781 and Digital Product Passport rollout.
\href{https://eur-lex.europa.eu/eli/reg/2024/1781/oj}{eur-lex.europa.eu/eli/reg/2024/1781/oj}

\bibitem{moda} Ministry of Digital Affairs, ROC (Taiwan). (2026). 2026
Presidential Hackathon International Track launches global call for entries.
\href{https://moda.gov.tw/en/press/press-releases/20076}{moda.gov.tw/en/press/press-releases/20076}

\bibitem{handbook} Ministry of Digital Affairs / Taipei Computer Association.
(2026, May). 2026 Presidential Hackathon International Track Handbook.
\href{https://presidential-hackathon.taiwan.gov.tw/en/international-track/}{presidential-hackathon.taiwan.gov.tw/en/international-track}

\bibitem{chanchin} Chan Chin C. Enterprise. ISO 14067 low-carbon steel
fasteners carbon footprint verification opinion statement.
\href{https://www.chanchinc.com/en/news/Taiwan-based_screw_manufacturer_05.html}{chanchinc.com/en/news}

\bibitem{ecobiz} Eco-Business. (2026, June). Taiwan collects first carbon fee
payments, plans higher rates and emissions trading pilot.
\href{https://www.eco-business.com/news/taiwan-collects-first-carbon-fee-payments-plans-higher-rates-and-emissions-trading-pilot/}{eco-business.com/news}

\bibitem{pmc} Chen, Y.-C., et al. (2025). Public--private partnership in
pipelining science of acute care ecosystem: Insights from Taiwan's Presidential
Hackathon. \emph{Learning Health Systems}.
\href{https://pmc.ncbi.nlm.nih.gov/articles/PMC12264364/}{pmc.ncbi.nlm.nih.gov/articles/PMC12264364}

\bibitem{offset} Ministry of Environment, ROC (Taiwan). Voluntary greenhouse
gas reduction offset information platform.
\href{https://carbonoffset.moenv.gov.tw/EnglishVersion}{carbonoffset.moenv.gov.tw/EnglishVersion}

\end{thebibliography}
