\clearpage
\phantomsection
\addcontentsline{toc}{section}{References}
\footnotesize
\begin{thebibliography}{99}\setlength{\itemsep}{2pt}

\bibitem{handbook} Ministry of Digital Affairs / Taipei Computer Association.
(2026, May). 2026 Presidential Hackathon International Track Handbook.
\href{https://presidential-hackathon.taiwan.gov.tw/en/international-track/}{presidential-hackathon.taiwan.gov.tw/en/international-track}

\bibitem{cost} CoST --- Infrastructure Transparency Initiative. CoST Honduras
(SISOCS history, disclosure rates, project counts).
\href{https://infrastructuretransparency.org/where/cost-honduras/}{infrastructuretransparency.org/where/cost-honduras};
\href{https://infrastructuretransparency.org/news/cost-honduras-showcases-groundbreaking-tool-for-sustainable-infrastructure/}{2019 showcase}

\bibitem{ocpcartel} Open Contracting Partnership. (2019, August 23).
Cartelogy: A tool for fair competition and corruption-free public procurement
in Malaysia.
\href{https://www.open-contracting.org/2019/08/23/cartelogy-a-tool-for-fair-competition-and-corruption-free-public-procurement-in-malaysia/}{open-contracting.org}

\bibitem{ocpfiscal} Open Contracting Partnership. (2020). Teams from India and
Taiwan win this year's Presidential Hackathon with projects on health
procurement and social housing.
\href{https://www.open-contracting.org/news/teams-from-india-and-taiwan-win-this-years-presidential-hackathon-with-projects-on-health-procurement-and-social-housing/}{open-contracting.org}

\bibitem{ocpindia} Open Contracting Partnership. (2020, December 14). Setting
the sustainability standard for India's healthcare procurement; CivicDataLab,
Public Procurement program.
\href{https://www.open-contracting.org/2020/12/14/setting-the-sustainability-standard-for-indias-healthcare-procurement/}{open-contracting.org};
\href{https://civicdatalab.in/work/opencontracting/publicprocurement/}{civicdatalab.in}

\bibitem{abstreet} A/B Street project. GitHub organization and documentation
(project started 2018; current development focus).
\href{https://github.com/a-b-street/abstreet}{github.com/a-b-street/abstreet};
\href{https://abstreet.uk/services/}{abstreet.uk}

\bibitem{abinterview} OpenCage. Interview: Dustin Carlino --- A/B Street (on
nearly ending the project and its continuation); The Alan Turing Institute,
researcher profile.
\href{https://blog.opencagedata.com/post/openstreetmap-interview-ab-street}{blog.opencagedata.com};
\href{https://www.turing.ac.uk/people/researchers/dustin-carlino}{turing.ac.uk}

\bibitem{pres2021} Office of the President, ROC (Taiwan). (2021). President
Tsai attends Presidential Hackathon award ceremony.
\href{https://english.president.gov.tw/News/6208}{english.president.gov.tw/News/6208}

\bibitem{hist2023} Presidential Hackathon International Track --- official
history pages (2022--2023 team descriptions, incl.\ BRSDM@Er-Lin biochar
platform and B.E.N.Z.\ GIS urban-forest project).
\href{https://presidential-hackathon.taiwan.gov.tw/history/2023/en/international-track/index.html}{presidential-hackathon.taiwan.gov.tw/history/2023}

\bibitem{moda2023} Ministry of Digital Affairs. (2023). New record of 2023
Presidential Hackathon: Team Taiwan--India and Team Thai selected as
outstanding teams.
\href{https://moda.gov.tw/en/press/press-releases/6463}{moda.gov.tw/en/press/press-releases/6463}

\bibitem{hyson} Hyson Technology. Intelligent aquaculture product line
(commercial site).
\href{https://www.hysontech.tw/products/8/1}{hysontech.tw/products/8/1}

\bibitem{moda2024} Ministry of Digital Affairs. (2024). Presidential Hackathon
promotes international collaboration to accelerate environmental
sustainability through technology.
\href{https://moda.gov.tw/en/press/press-releases/14882}{moda.gov.tw/en/press/press-releases/14882}

\bibitem{greenhope} GreenHope. Web3.0: The new era of value exchange
(commercial site).
\href{https://www.greenhope.com.tw/}{greenhope.com.tw}

\bibitem{focuscrop} Focus Taiwan / CNA. (2025, December 14). Taiwan--France
and India teams win 2025 Presidential Hackathon international track.
\href{https://focustaiwan.tw/politics/202512140012}{focustaiwan.tw/politics/202512140012}

\bibitem{pres2025} Office of the President, ROC (Taiwan). (2025). President
Lai attends 2025 Presidential Hackathon awards ceremony.
\href{https://english.president.gov.tw/News/7057}{english.president.gov.tw/News/7057}

\bibitem{moda2026} Ministry of Digital Affairs. (2026). 2026 Presidential
Hackathon International Track launches global call for entries (returning
Teams of Excellence: GreenhopeBCTW, CropNow, Beyond Hearing).
\href{https://moda.gov.tw/en/press/press-releases/20076}{moda.gov.tw/en/press/press-releases/20076}

\bibitem{pmc} Chen, Y.-C., et al. (2025). Public--private partnership in
pipelining science of acute care ecosystem: Insights from Taiwan's
Presidential Hackathon. \emph{Learning Health Systems}.
\href{https://pmc.ncbi.nlm.nih.gov/articles/PMC12264364/}{pmc.ncbi.nlm.nih.gov/articles/PMC12264364}

\bibitem{mygov} MyGOV --- The Government of Malaysia's Official Portal.
Malaysian award-winning team at the 2019 Taiwan Presidential Hackathon
(``Mentadak'') --- source of the 2019 honor-roll discrepancy flagged in
Section 3.5.
\href{https://www.malaysia.gov.my/portal/content/30753}{malaysia.gov.my/portal/content/30753}

\end{thebibliography}
