\section{The Solution: CarbonPass in Action}\label{sec:solution}

\subsection{Sixty seconds in the life of the user}

Mr.~Lin, Gangshan, 61, opens LINE. The assistant greets him in Taiwanese and
asks for a photo of last month's Taipower bill. He photographs it, then the
steel wire-rod invoices, and answers three plain questions about last month's
production. Ninety seconds later he has: a \textbf{carbon data pack} for his
screws, per customs code, formatted to the European Commission's template and
flagged line-by-line for the verifier; a \textbf{one-screen argument} he can
forward to his Rotterdam buyer --- \emph{your cost with my data:
$\approx$EUR~150/t; without it: EUR~450--750/t and rising}; and a
\textbf{suggestion}: shift the heat-treatment furnace to the 02:00--06:00
window this month, saving an estimated NT\$ amount on the bill and a stated
number of kilograms of CO$_2$ --- both of which flow into next quarter's pack
automatically. No portal. No consultant. No data leaving his building.

\subsection{The three AI systems behind the conversation}

\begin{table}[htbp]
\caption{The CarbonPass pipeline: from shoebox documents to market access}
\label{tab:pipeline}
\small
\begin{tabularx}{\textwidth}{@{}p{0.21\textwidth}X@{}}
\toprule
\textbf{Stage} & \textbf{What happens} \\
\midrule
Inputs the SME already has & Taipower bills, material invoices, production records --- photographed in LINE, in Mandarin/Taiwanese \\
Document intelligence + allocation & Vision-language parsing of messy, mixed-format documents; facility energy allocated across product lines and CN codes with quantified uncertainty \\
Compliance rules engine & The EU methodology (simple/complex goods, precursors, default tables from the 2,400-page regulation\cite{omm}) encoded into field-level guidance and the Commission's template structure \\
Grid-aware scheduler & Hourly grid carbon intensity computed live from Taipower's open 10-minute generation feed\cite{taipowerdata} + time-of-use tariffs\cite{taipower} $\to$ MILP + reinforcement-learning shift plans for flexible loads \\
Outputs & CBAM data pack per CN code; organizational inventory; buyer-cost delta screen; monitored before/after reduction ledger \\
\bottomrule
\end{tabularx}
\end{table}

\textbf{1. Document intelligence with allocation reasoning.} Anyone can OCR a
bill. The hard problem --- the one that decides CBAM compliance --- is
\emph{allocation}: splitting one facility-wide electricity number across
dozens of screw variants, per customs code, defensibly. CarbonPass treats this
as a constrained-inference problem over production volumes, machine ratings
and operating-hour priors, and attaches a quantified uncertainty to every
line, so a human verifier sees not just a number but how solid it is. This is
the step no existing calculator attempts (Section~\ref{sec:diff}).

\textbf{2. A regulation, compiled.} The EU's methodology --- simple versus
complex goods, precursor emissions, punitive default tables --- is encoded as
a rules engine that fills the Commission's own communication template and
marks each field \emph{actual / default / needs attention}. The AI does not
replace the accredited verifier; it hands the verifier (and the EU importer) a
structured, auditable file instead of a shoebox of paper.

\textbf{3. A scheduler that reads the national grid.} Taiwan publishes
every generating unit's output at 10-minute resolution as open
data\cite{taipowerdata}. CarbonPass converts that feed into an hourly
carbon-intensity curve for the whole grid, overlays Taipower's time-of-use
prices, and optimizes when the factory's flexible loads run --- subject to the
owner's order deadlines, stated in chat. Savings are measured on the meter,
logged in a before/after ledger structured to the baseline-and-monitoring
logic of ISO~14064-2, and feed the next data pack. \textbf{Measurement and
mitigation reinforce each other --- the tool does not just report carbon, it
removes some.}

\textbf{Privacy as architecture, not promise.} Taiwanese SMEs rightly treat
energy and production data as trade secrets. CarbonPass is \emph{local-first}:
parsing and computation run on the factory's own device or premises; only the
outputs the owner chooses to send ever leave. The roadmap --- federated
benchmark learning across the cluster, hardware-backed confidential computing
--- follows privacy-preserving patterns Taiwan's own financial sector has
already normalized, and aligns with the national Trusted-AI posture.

\subsection{Stakeholders and their roles}

\begin{table}[htbp]
\caption{Stakeholders, roles, and what each gains}
\label{tab:stakeholders}
\small
\begin{tabularx}{\textwidth}{@{}p{0.28\textwidth}X@{}}
\toprule
\textbf{Stakeholder} & \textbf{Role and benefit} \\
\midrule
Fastener SME owners (target audience) & Primary users; retain EU customers, cut power costs, gain a standing carbon capability \\
EU importers and their declarants & Receive template-ready supplier data; avoid punitive defaults\cite{omm} \\
TIFI ($\sim$700 member firms) and MIRDC & Pilot recruitment, domain validation, cluster-scale rollout channel\cite{goebel} \\
MOENV / Climate Change Administration & Their CBAM help platform\cite{tpt-cbam} gains the computational layer it lacks; carbon-fee readiness grows in the SME base \\
MOEA / SMESA & CAAS education stack\cite{caas} gains an execution tool; supports SME competitiveness programs \\
Taipower & Its open data and AMI infrastructure\cite{taipower,taipowerdata} become directly value-generating for small industry \\
Accredited verifiers & Receive structured, uncertainty-annotated files instead of raw paper --- faster, cheaper verification \\
Banks (green finance) & Verified SME carbon data for sustainability-linked lending \\
\bottomrule
\end{tabularx}
\end{table}
